TOI based ProVisioNet

### 2021-08-30 01_studies/01_Laborstudie ProVisioNET/R script/ProVisioNet_TOI-based_data.Rmd

```{r}
library(needs)
needs(tidyverse,
      psych)
```

@@

```

@@

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur$TOI != "Lesson"],
     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur$TOI != "Lesson"],
          method = "pearson")

@@

plot(x = df_cappa_dur$Duration_of_interval_EH[df_cappa_dur != "Lesson"],
     y = df_cappa_dur$Duration_of_interval_RD[df_cappa_dur != "Lesson"])
```

@@

```{r}
cor.test(x = df_cappa_start$Start_of_interval_EH[df_cappa_start$TOI != "Lesson"],
     y = df_cappa_start$Start_of_interval_RD[df_cappa_start$TOI != "Lesson"],
          method = "pearson")

@@

plot(x = df_cappa_start$Start_of_interval_EH[df_cappa_start != "Lesson"],
     y = df_cappa_start$Start_of_interval_RD[df_cappa_start != "Lesson"])
```

>>>>

```{r}
library(needs)
needs(tidyverse,
      psych,
      ggthemes
      )
```

@@

# In seconds

df_cappa_dur$Duration_of_interval_EH <- round(df_cappa_dur$Duration_of_interval_EH/1000,
                                              digits = 2
                                              )

df_cappa_dur$Duration_of_interval_RD <- round(df_cappa_dur$Duration_of_interval_RD/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_EH <- round(df_cappa_start$Start_of_interval_EH/1000,
                                              digits = 2
                                              )

df_cappa_start$Start_of_interval_RD <- round(df_cappa_start$Start_of_interval_RD/1000,
                                              digits = 2
                                             )
```

#
```{r}
fun_1 <- function(x) {
    y <- x
    return(y)
  }
```

@@

```{r}
cor.test(x = df_cappa_dur$Duration_of_interval_EH,
     y = df_cappa_dur$Duration_of_interval_RD,
          method = "pearson")

@@

# Lesson is significant longer and gives a biased view on the points.

ggplot(data = filter(df_cappa_dur,
                     TOI != "Lesson"),
       mapping = aes(x = Duration_of_interval_RD,
                     y = Duration_of_interval_EH
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Duration coded by RD",
       y = "Duration coded by EH",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```

@@

```{r}
cor.test(x = df_cappa_start$Start_of_interval_EH,
     y = df_cappa_start$Start_of_interval_RD,
          method = "pearson")

@@

ggplot(data = filter(df_cappa_start,
                     TOI != "Lesson"),
       mapping = aes(x = Start_of_interval_RD,
                     y = Start_of_interval_EH
                     )
       ) +
  geom_point(size = 2) +
  geom_abline(intercept = 0,
              slope = 1,
              color = "red",
              linetype = 3
              ) +
  labs(x = "Start coded by RD",
       y = "Start coded by EH",
       title = "Inter-coder reliability"
       ) +
  theme_minimal()
```
